Local to global N input modelling

### 2025-05-16 08_manuscript/08_manuscript.qmd
Parameter name fixes

| $pk$ | `r unname(params['pk'])` | d$^{-1}$ | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |

@@

| $m$ | `r unname(params['m'])` | - | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] | 
| $n$ | `r unname(params['n'])` | - | Weight exponent for catabolism | @baldan_r_2018 |

@@

| $a$ | `r unname(params['a'])` | J g tissue$^{-1}$ | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
| $k$ | `r unname(params['k'])` | - | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
| $eff$ | `r unname(params['eff'])` | - | Food ingestion efficiency | Range: 95-97% ingestion efficiency [@uglem_does_2020] | 

@@

| $mort$ | `r unname(params['mortmyt'])` | d$^{-1}$ | Natural mortality rate | @tvete_towards_2023 |
: Growth parameters for Atlantic salmon {#tbl-params}

>>>>

| pk | `r unname(params['pk'])` | d$^{-1}$ | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |

@@

| m | `r unname(params['m'])` | - | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] | 
| n | `r unname(params['n'])` | - | Weight exponent for catabolism | @baldan_r_2018 |

@@

| a | `r unname(params['a'])` | J g tissue$^{-1}$ | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
| k | `r unname(params['k'])` | - | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
| eff | `r unname(params['eff'])` | - | Food ingestion efficiency | Range: 95-97% ingestion efficiency [@uglem_does_2020] | 

@@

| $\overline{F}$ | `r unname(params['overFmean'])` | g g$^{-1}$ fish$ | Overfeeding rate mean |    |
| $\Delta{F}$ | `r unname(params['overFdelta'])` | g g$^{-1}$ fish$ | Overfeeding rate standard deviation |    |
| mort | `r unname(params['mortmyt'])` | d$^{-1}$ | Natural mortality rate | @tvete_towards_2023 |
: Model growth parameters for Atlantic salmon {#tbl-params}
